### 2019-05-07 README.Rmd
updated DOI for preprint

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/AssessBCGPolicyChange/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/AssessBCGPolicyChange)
[![Paper](https://img.shields.io/badge/Paper-10.1101/567511-lightgreen.svg)](https://doi.org/10.1101/567511)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2635687.svg)](https://doi.org/10.5281/zenodo.2635687)

>>>>

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/AssessBCGPolicyChange/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/AssessBCGPolicyChange)
[![Paper](https://img.shields.io/badge/Paper-10.1101/624916-lightgreen.svg)](https://doi.org/10.1101/624916)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2635687.svg)](https://doi.org/10.5281/zenodo.2635687)
